# How S3 and S4 methods work
Both S3 and S4 accomplish the goals of encapsulation and polymorphism. In fact, the polymorphism is accomplished in nearly the same way.

In object-oriented programming, a *`method`* is a function that belongs to an object. R's handling of methods is an extremely important way that the language is flexible and intuitive. When you call the `plot()` function, you call a generic method that decides what specific method should be used based on the object's class name. First, let's recall that you can see the code for a function by writing the function name without parentheses:

```{r plot-introspection}
# function without parentheses prints the code:
plot
```

The `UseMethod("plot")` part causes R to select from all the functions named like `plot.<classname>()`, which you can list this way:

```{r list-methods}
methods(plot)
```

Let's see the code that actually does the work of `plot.lm()` and `plot.merMod()`:

```{r plot-code}
stats:::plot.lm

lme4:::plot.merMod
```


